---
title: "Project Description"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
source('Part5_source.R')

```


SavingsDashboard
=====================================  

Row
---------------------

### Map of savings

```{r}

plotMap11

```

Row
---------------------

### Table of savings

```{r}
library(DT)
datatable(Savings)


```


### Description

Data on the savings ratio 1960–1970. <br>
A data frame with 50 observations on 5 variables. <br>

* [,1]	 sr	 numeric	 aggregate personal savings
* [,2]	 pop15	 numeric	 % of population under 15
* [,3]	 pop75	 numeric	 % of population over 75
* [,4]	 dpi	 numeric	 real per-capita disposable income
* [,5]	 ddpi	 numeric	 % growth rate of dpi


CarsDashboard
=====================================

Row {data-height=200}
-----------------------

### Average Hp

```{r}
average_hp <- round(mean(mtcars$hp), 0)
gauge(average_hp, min = 0, max = max(mtcars$hp), symbol = 'hp', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

### Average mpg
```{r}
average_mpg <- round(mean(mtcars$mpg), 0)
gauge(average_mpg, min = 0, max = max(mtcars$mpg), symbol = 'mpg', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```


Row {data-height=200}
-----------------------


### Number of Brands

```{r}

Brands <- length(mtcars_summary$Brand)
valueBox(Brands, icon = "glyphicon-pencil")


```

### Number of Cars with hp above 100

```{r}
cars_summary_hp <- mtcars %>%
  filter(hp>100)

hp100 <- length(cars_summary_hp)
valueBox(paste(hp100, "/", dim(mtcars)[1], sep = ""), icon = "glyphicon-star")


```

Row {data-height=600}
-----------------------

### Boxplot

```{r}

mtcars_box_plot

```


